Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

Title count per decade:

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
df2 <- df0 %>% group_by(publication_decade, catalog) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() + facet_grid(catalog ~ .) +
     ggtitle("Title count timeline")
print(p)
```

>>>>

Paper consumption per decade:

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE))
p <- ggplot(df2, aes(x = publication_decade, y = paper)) +
     geom_bar(stat = "identity") + #scale_y_log10() +
     facet_grid(catalog ~ .) +
     ggtitle("Paper consumption timeline")
print(p)
```
